A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-29 UAM2014/Article/article.tex
la2pdf commit - 2014:04:29	11:52:05	(Tue29.Apr)

We have developed a simulator for synthetic aperture sonar (SAS) that creates object templates very quickly with the aid of the massive computing power in graphics processing units (GPUs). It uses OpenGL to render a optical 2D image and depth map from the 3D model and seafloor representation, and OpenCL compute a sonar template based on this.

By coincidence this implementation is not so different from the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC). They both take advantage of graphics processing to render a 2D image from 3D models, are designed for side-looking sonar, and assume a Lambertian scattering model. However, SIGMAS+ is not designed for creating object templates, and adds e.g. noise to the images for them to more closely

@@

Citations
\begin{itemize}
\item Midelfart/Midtgaard: Adaptive templates \cite{Midelfart2010}
\item Simulation of sidescan images (Bell thesis \cite{Bell1997}, pre-work by V.Blake \cite{Blake1993})
\item NURC SIGMAS+ (Coiras GPU article at OCEANS 2009 \cite{Coiras2009a}, Coiras on SIGMAS maths \cite{Coiras2009b})
\end{itemize}

>>>>

We have developed a simulator for synthetic aperture sonar (SAS) that creates object templates very quickly with the aid of the massive computing power in graphics processing units (GPUs). It uses OpenGL to render a optical 2D image and depth map of scene with a custom 3D model of the object and seafloor, and OpenCL to post-process this data to form sonar templates.

By coincidence our implementation is not so different from the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC)~\cite{Coiras2009a, Coiras2009b}. They both take advantage of OpenGL to render a 2D image from 3D models, are designed for side-looking sonar, and assume a Lambertian scattering model. However, while SIGMAS+ is geared more towards realistically looking sonar images and includes effects such as noise, we do not. Also, SIGMAS+ sum images obtained from multiple OpenGL rendering passes to create the sonar image, while we render once and tailor the sonar image with the flexibility of OpenCL.

does not use OpenCL but a OpenGL a multi-pass technique, and includes ting  W
is not designed for creating object templates, and adds e.g. noise to the images for them to more closely

@@

Citations
\begin{itemize}
\item Midelfart/Midtgaard: Adaptive templates \cite{Midelfart2010}
\item Simulation of sidescan images (Bell thesis \cite{Bell1997}, pre-work by V.Blake \cite{Blake1993})
\end{itemize}
